Empirical Check of Machine Homogeneity on Timing Protocol

### 2018-05-16 pt_characterization/machine_cons_check/post_exp.tex
Added INC13

>>>>

\newpage
\clearpage
\subsection{Power Strip Influence~\label{sec:sodb8}}

A short description of the runs we used for this experiment are exhibited in Table~\ref{tab:exp_notes4}.

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8}  (plugged into {\em bottom left} power strip) &  INC13 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb8}  (plugged into {\em the upper left} power strip) &  INC13 & Runs of 1,000 samples & 2018-04-28 $\sim$2018-04-30\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes4}}
\end{table}

\begin{figure}[H]
	\centering
	\subfigure[PT frequency on INC13 on {\tt sodb8}  (plugged into {\em bottom left} power strip) (copied from Fig.~\ref{fig:s8_inc13_dist})]{
		\includegraphics[scale=0.43]{newer_exp/sodb8_INC13_0_dist.eps}
		\label{fig:s8_inc13_dist_before}
	}
	\subfigure[PT frequency on INC13 on {\tt sodb8}  (plugged into {\em the upper left} power strip)]{
		\includegraphics[scale=0.43]{new_INC_data_s9/s8_INC13_dist.eps}
		\label{fig:s8_inc13_dist_after}
	}
	\caption{PT Histograms on INC13 on {\tt sodb8} Before and After Power Strip Relocation\label{fig:power_strip}}
\end{figure}
